Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
begin writing generic code to compare nldas to county weather data

```{r}
county_timeseries(fips = ike_top[1:2], 
                  percent_coverage = 0, 
                  date_min = "2008-09-01", 
                  date_max = "2010-09-14", var = "PRCP", 
                  out_directory = "~/tmp/ike_ex")

>>>>

```{r}
county_timeseries(fips = ike_top[1:2], 
                  percent_coverage = 0, 
                  date_min = "2008-09-01", 
                  date_max = "2010-09-14", var = "PRCP", 
                  out_directory = "~/tmp/ike_ex")
ike_1 <- readRDS("~/tmp/ike_ex/12087.rds")
ike_1 <- ike_1 %>%
        select(date, prcp) %>%
        filter(date %in% seq(from = as.Date("2008-09-01"), to = as.Date("2008-09-14"), by = 1))
data(rain)
ike_rain <- subset(rain, rain$storm_id == "Ike-2008" & rain$fips == "12087")
data("closest_dist")
keys_cd <- subset(closest_dist, closest_dist$storm_id == "Ike-2008" & closest_dist$fips == "12087")
keys_cd <- keys_cd$closest_date
ike_1 <- ike_1 %>%
        filter(date %in% seq(from = as.Date("2008-09-07"), to = as.Date("2008-09-10"), 1))
#assuming the prcp is in inches
ike_1$prcp_mm <- convert_precip(ike_1$prcp, "inches", "mm")
ike_sum <- sum(ike_1$prcp_mm)
ike_nldas_sum <- subset(ike_nldas, ike_nldas$fips == "12087")
ike_nldas_sum <- ike_nldas_sum$tot_precip
```
